The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-03-03 src/ms.tex
editing session
Co-authored-by: Marten van Kerkwijk <mhvk@astro.utoronto.ca>
Signed-off-by: nstarman <nstarkman@protonmail.com>

The \astropypkg core package is mature and stable, in that many features have
been part of the core package for years with (purposefully) few changes to the
software interface.  This maturity and stability allows for the broader
astronomy \python community to rely upon the \astropypkg core package and build
specialized packages within the Astropy ecosystem.  Even many non-astronomical
\python libraries have come to rely on \astropypkg. The relationship between
\astropy and the \python-using community is reciprocal, with the evolving needs
of the community and the maturation of the broader scientific \python ecosystem
driving much of the development of the \astropypkg core package.

@@

New features present a particular difficulty for a mature package such as
\astropypkg, because it is difficult to know {\em a priori} what the best
interface will be, and hard to address all possible use cases in one round of
development, even within \astropypkg\ itself.

New features come in various forms, from new submodules providing wholly new
capabilities, to larger additions to existing submodules, to large rewrites of
the interface of modules. This range is spanned by five main new features that
entered the \astropypkg core since the previous summary
\citepalias{astropy:2018}. In our descriptions of each we include how we hope
the new feature will evolve. Ultimately, in a user-driven project like \astropy,
development depends primarily on the priorities of contributors.

@@

In general, proper error propagation is difficult, and often it is best to use
Monte Carlo methods.  The new \astropysubpkg{uncertainties} sub-package is our
first step towards enabling seamless error propagation.  The package allows one
to generate, for each variable, randomly drawn samples in a
\astropyDistribution, and then propagate these by passing them through the
normal analysis, producing a \astropyDistribution\ of final results that can be
inspected.

This \astropyDistribution\ can be any type of array, including a
\astropyQuantity. The goal is to ensure \astropyDistribution\ can be seamlessly
used to instantiate other \astropypkg classes as well, such as \astropySkyCoord,
\astropyTime, and \astropyCosmology.

A plan for future development of \astropysubpkg{uncertainties} is to support
error propagation, tracking covariances, where the uncertainties are assumed to
be normally distributed rather than approximated by Monte-Carlo means. One
implementation problem to be solved is when to {\em stop} tracking covariances.
For instance, a simple operation such as subtracting the mean from $N$ data
points implies that all data points are now covariant with each other, i.e., one
has to carry $N\times N$ covariances.  For a large image, that becomes not just
pointless but also prohibitive in terms of memory and CPU usage.

\paragraph{Masked quantities}  It can be useful to mask bad data.  How one
supports masked data involves a number of choices, such as whether one indicates
data values are bad by a separate flag or by replacing them with a special
value, such as ``Not a Number'' (NaN).  In \astropypkg, both approaches have
been used: a flag for masked columns in \astropyTable, mask flags and bitmaps
for N-dimensional data in \astropysubpkg{nddata}, and replacing elements with
NaN in \astropyTime.  However masked quantities were poorly supported, making it
difficult to use masks in a \astropyQTable (in which \astropyQuantity\ is used
for all columns with units).

Unfortunately, the \texttt{MaskedArray} class from \package{numpy} could not be
used because its design made it a wrapper around any subclass. Therefore
another class could not use it as an alternative to a regular data array.
% Nathaniel: I find this topic sentence a bit confusing.
For quantities, \texttt{MaskedArray} does not work because a masked value does
not mean the unit is unknown. Consequently, a new \astropyMasked\ class was
designed, based on a framework very similar to that of \astropyDistribution,
making it easy to create masked instances of other classes.  In particular,
\astropyMasked\ can be used to create masked quantities for \astropyQTable,
enabling full support for reading and writing different file types.

@@

Also part of \astropysubpkg{timeseries} are common analysis routines, including
Lomb-Scargle and box-least-squares periodogrammes.

\paragraph{Spectral Coordinates} Measurements are often taken at specific
``spectral coordinates,'' be they frequencies, wavelengths, or photon energies.
\astropyQuantity\ can represent these physical quantities and convert between
them via dedicated equivalencies. The new \astropySpectralCoord\ builds on
\astropyQuantity\ by providing a more straightforward interface: baking in these
equivalencies and those for Doppler velocities. Furthermore,
\astropySpectralCoord\ can be made aware of the observer and target reference
frames, allowing transformation from telescope-centric (or topocentric) frames
to Barycentric or Local Standard of Rest (LSRK and LSRD) velocity frames.

@@

Units were also integrated further within \astropypkg. For an already-defined unit-less
\astropyModel, e.g. those imported from another library, \astropymodeling can
now coerce units.
% TODO! transition words
A new module – \astropycosmologyunits – has been added to the cosmology
sub-package for defining and collecting cosmological units and equivalencies.
The unit \texttt{littleh} and equivalency
\astropyapidoc{cosmology.units.with_H0}{with\_H0} are deprecated from the main
\astropyunits sub-package and moved to \astropycosmologyunits. A new unit,
\texttt{redshift}, has been added for tracking factors of cosmological redshift. To
correctly use redshift units in dimensional analysis, \texttt{redshift} is
\astropyapidoc{cosmology.units.dimensionless_redshift}{treated as dimensionless}
by default. To convert between redshift and other cosmological distance
measures, e.g. CMB temperature or comoving distance, the equivalency
\astropyapidoc{cosmology.units.with_redshift}{with\_redshift}
has also been added. This equivalency is actually a composite of other equivalencies,
which may be used separately.

@@

Within \astropypkg and \python there are numerous ways to represent and store
array-valued data. Some of the differences are historical:
\astropyapidoc{table.Column}{table.Column} and
\astropyapidoc{io.fits.Column}{io.fits.Column} are not the same. Some
differences are computational: \package{numpy}, \package{cupy}, and
\package{dask} arrays are almost API identical, but are optimized for different
compute needs. Lastly, some differences are inherent: \astropyQuantity,
\astropyTime\, and \astropySkyCoord\ represent fundamentally different types of
objects.

\astropy believes that however array-valued data is stored, it should still be
usable as a column in a table. A well defined protocol for mixin-columns has
been developed for \astropytable and \astropyfits tables, allowing the original
object to be used as a column with a familiar API, and to ``round-trip'' through
tables with no loss of data or attributes. With this protocol, it is now
possible to store standard \astropyTableColumn\ objects to a FITS table
\href{https://docs.astropy.org/en/stable/io/fits/api/hdus.html}{HDU}. It is also
possible to store \astropy native objects -- including \astropyTime,
\astropyQuantity, and \astropySkyCoord --  within a \astropyTable. For objects
not already covered by the mixin protocol, functions can be registered with
\astropyTable\ to convert on-the-fly any array-like object into a mixin column.
As an example, the mixin functions are used to integrate \package{dask} arrays
with \astropyTable, allowing cloud-stored or cluster-scale data to be used as a
column in a \astropyTable.

@@

The FITS standard was extended to rigorously describe time coordinates in the
World Coordinate System (WCS) framework \citep{FITS-Time:2015}. Compared to
other coordinates in the WCS framework, time requires more metadata: format,
scale, position, reference, etc. This metadata had to be manually specified and
the nuances understood by the user. \astropyfits could store this data in a
standard \astropyFitsColumn\ (for details, see the
\href{https://docs.astropy.org/en/stable/io/fits/index.html}{FITS
documentation}), but would not ``understand'' the metadata and attributes.
Thankfully, through the support of the
\href{https://summerofcode.withgoogle.com/archive/2017/projects/4778482366152704}{Google
Summer of Code} 2017 program, the \astropyfits package now allows \astropyTime\
as a `mixin' column. \astropyTime\ columns in FITS tables ``understand'' the
metadata while also providing a similar interface as the regular
\astropyFitsColumn\ objects. With \astropyTime\ columns, \astropy ensures that
time coordinates are stored according to the FITS standard in a consistent
manner and can be read/written without loss of information. For backward
compatibility with manual systems, this feature may be turned off, but it is
recommended to update. To learn more about this project, please see the final
report,
\href{https://aaryapatil.wordpress.com/2017/08/28/a-mixin-protocol-for-seamless-interoperability/}{A
mixin protocol for seamless interoperability}.

@@

\astropy now supports reading and writing tables in the American Astronomical
Society Journals' Machine-Readable Table (MRT) format. This ASCII format has
long been missing, and we are pleased that this year's Google Summer of Code
project adds MRT to \astropyTable\ I/O.  
For details, see the
\href{https://docs.astropy.org/en/stable/io/ascii/write.html#cds-mrt-format}{Machine-Readable
Table Format} section of \astropy's documentation. In addition, \astropyTable\ may also read from and write to
\href{https://asdf-standard.readthedocs.io/en/latest/}{ASDF},
\href{https://docs.astropy.org/en/stable/io/unified.html#table-io-parquet}{Parquet},
and \href{https://wwwastro.msfc.nasa.gov/qdp/}{QDP} formats.

The \href{https://github.com/astropy/astropy-APEs/blob/main/APE6.rst}{ECSV
standard} has been updated to version 1.0, adding support for reading and
writing \astropyTable\ with three additional data subtypes. First, it adds
multidimensional column data (both masked and unmasked) with fixed dimensions in
all table cells. Second, it adds multidimensional column data with
variable-dimension arrays similar to FITS variable-length arrays. Third, it adds
object-type columns with simple \python objects.

@@

% TODO! better transition
\astropyiosubpkg{registry} is a powerful way to define input and output (I/O)
functions for \astropypkg objects, such as reading from or writing to a file.
\astropy uses this internally for the I/O methods in \astropyTable\ and
\astropyCosmology\ (I/O added v5.0+), and users can register custom I/O to extend
the options on these classes.

As of Astropy 5.0, the I/O registry submodule has switched to a class-based
architecture and has been refactored to allow read-only, write-only, and
read-write registries. Additionally, the registry submodule no longer assumes an
object has \astropy-style \texttt{read} and \texttt{write} methods when trying
to read or write that object. These two improvements enable a number of new use
cases for \astropyiosubpkg{registry}, which we hope have community adoption.
First, the class-based architecture allows for the creation of custom
registries. One application is in \astropycosmology, which has two different
\textit{kinds} of registries for \astropyCosmology: one for reading and writing
files, and another for converting between python objects. Second, \textit{any}
kind of object is now compatible with \astropyiosubpkg{registry}. Using
\astropyiosubpkg{registry} for custom classes means a developer does not have to
create a whole new I/O system and can offer to the user a unified and familiar
API.

@@

An important focus of \astropy has been to increase the precision and accuracy
of its functionality, while, where appropriate, making sure results obtained
using older versions of \astropypkg are reproducible. Within each section below
we include in our descriptions how old results may be reproduced. The primary
means are with configuration file options, and settings on runtime configuration
objects called \astropyScienceState. Notable improvements to \astropypkg have
been made to \astropytime, \astropyconstants, \astropycoordinates, and
\astropycosmology, and we describe each in turn.

@@

Measurements of physical constants (and the units defined from them) improve
over time. Periodically the standardized systems of units and constants are
updated to reflect these improvements. For instance, in 2019 the SI system was
redefined \citep{NIST2019}, with an accompanying update to the physical
constants in
\href{https://codata.org/initiatives/data-science-and-stewardship/fundamental-physical-constants/}{\texttt{SI/CODATA
2018}}. \astropyconstants now defaults to use the \texttt{SI/CODATA 2018}
values, with the relation between units in \astropyunits based upon these
constants. Most of \astropypkg and affiliate packages build upon \astropyunits,
so this update has far-reaching effects across the \astropy ecosystem and
astronomy community.

For reproducibility, \astropypkg allows the constants' (and therefore units')
definitions to be rolled back to prior values, e.g. to the
\texttt{SI/CODATA 2014} values.
% CITATION
The constants' and units' definitions are set by configuration file as well as a
\astropyScienceState\. For work sensitive to the values of the fundamental
constants we recommend including with the work an \astropy configuration file,
which specifies the set of constants used.

@@

Since \citealt{astropy:2018} the following cosmology realizations have been
added:
\href{http://docs.astropy.org/en/stable/api/astropy.cosmology.WMAP1.html}{\texttt{WMAP1}}
from WMAP First Year \citep[Table 7: WMAP + CBI + ACBAR + 2dFGRS +
Lya]{WMAP1Year:2003};
\href{http://docs.astropy.org/en/stable/api/astropy.cosmology.WMAP3.html}{\texttt{WMAP3}}
from WMAP Three Year \citep[Table 6: WMAP + SNGold]{WMAP3Year:2007};
\href{http://docs.astropy.org/en/stable/api/astropy.cosmology.Planck15.html}{\texttt{Planck15}}
from Planck 2015 \citep[Table 4: TT, TE, EE + lowP + lensing +
ext]{Planck2015XIII:2016};
and \href{http://docs.astropy.org/en/stable/api/astropy.cosmology.Planck18.html}{\texttt{Planck18}}
from the Planck 2018 best-fit cosmological parameters \citep[Table 2: TT, TE, EE
+ lowE + lensing + BAO]{Planck2018VI:2020}.

@@

Being able to describe the position of objects, i.e. their coordinates, is
fundamental across many knowledge domains. \astropypkg provides
\astropycoordinates for working with low-level positional and velocity data all
the way to high-level coordinate objects with reference frames, atmospheric
information, and more. A central feature of \astropycoordinates is the ability
to transform data between reference frames, e.g. \astropyICRS\ \citep{ICRS:1997}
to \astropyGalacticLSR\ \citep{GalacticLSR:2010}. However, there have been some
historical limitations for spatially proximate transformations, impacting the
usefulness of \astropycoordinates for ground-based telescopes and intra-solar
astronomy. Transformations in the \astropyAltAz\ frame were reasonably precise
for very distant objects, but wrong by up to several arcseconds for e.g., the
location of the moon. Now these transformations are much more precise, down to
the milliarcsecond level. Similar precision improvements were made to the
\astropyapi{coordinates.builtin_frames.HADec}{Hour Angle-Declination}
frame transformations. Additionally,
\astropyapi{coordinates.builtin_frames.BaseEclipticFrame}{Ecliptic frames}
and associated transformations have been updated to correctly reflect the “true”
(precession but not nutation) and “mean” (both precession and nutation)
terminology.

For Galactic astronomers, the \astropyGalactocentric\
\astropyapi{coordinates.galactocentric_frame_defaults}{frame defaults}
have been updated to include more recent measurements (tabulated in the
\href{https://docs.astropy.org/en/stable/api/astropy.coordinates.galactocentric_frame_defaults.html#astropy.coordinates.galactocentric_frame_defaults.references}{\texttt{frame\_defaults.references}}
attribute). For reproducibility, old definitions are still available, and will
continue to be so as \astropypkg is updated with forthcoming measurements of the
Galactic center, solar motion, etc.

>>>>

The \astropypkg core package is mature and stable, in that many features have
been part of the core package for years with purposefully few changes to the
software interface.  This maturity and stability allows for the broader
astronomy \python community to rely upon the \astropypkg core package and build
specialized packages within the Astropy ecosystem.  Even many non-astronomical
\python libraries have come to rely on \astropypkg. The relationship between
\astropy and the \python-using community is reciprocal, with the evolving needs
of the community and the maturation of the broader scientific \python ecosystem
driving much of the development of the \astropypkg core package.

@@

New features present a particular difficulty for a mature package such as
\astropypkg, because it is difficult to know {\em a priori} what the best
interface will be, and hard to address all possible use cases in one round of
development, even within \astropypkg\ itself. New features come in various forms,
from new submodules providing wholly new capabilities, to larger additions to
existing submodules, to large rewrites of the interface of modules. This range
is spanned by five main new features that entered the \astropypkg core since the
previous summary \citepalias{astropy:2018}. In our descriptions of each we
include how we hope the new feature will evolve. Ultimately, in a user-driven
project like \astropy, development depends primarily on the priorities of
contributors.

@@

Error propagation is difficult, and often is best approximated using Monte Carlo
methods.  The new \astropysubpkg{uncertainties} sub-package is our first step
towards enabling seamless error propagation.  The package allows one to
generate, for each variable, randomly drawn samples in a \astropyDistribution,
and then propagate these by passing them through the normal analysis, producing
a \astropyDistribution\ of final results that can be inspected. This
\astropyDistribution\ can be any type of array, including a \astropyQuantity.
The goal is to ensure \astropyDistribution\ can be seamlessly used to
instantiate other \astropypkg classes as well, such as \astropySkyCoord,
\astropyTime, and \astropyCosmology.

A plan for future development of \astropysubpkg{uncertainties} is to also
support error propagation, tracking covariances, for the case that uncertainties
are normally distributed rather than approximated by Monte-Carlo means. One
implementation problem to be solved is when to {\em stop} tracking covariances.
For instance, a simple operation such as subtracting the mean from $N$ data
points implies that all data points are now covariant with each other, i.e., one
has to carry $N\times N$ covariances.  For a large image, that becomes not just
pointless but also prohibitive in terms of memory and CPU usage.

\paragraph{Masked quantities}  It can be useful to mask bad data.  How one
supports masked data involves a number of choices, such as whether one indicates
data values are bad by a separate flag or by replacing bad data with a special
value, such as ``Not a Number'' (NaN).  In \astropypkg, both approaches have
been used: a flag for masked columns in \astropyTable, mask flags and bitmaps
for N-dimensional data in \astropysubpkg{nddata}, and replacing elements with
NaN in \astropyTime.  However masked quantities were poorly supported, making it
difficult to use masks in a \astropyQTable\ (in which \astropyQuantity\ is used
for all columns with units).

Unfortunately, the \texttt{MaskedArray} class from \package{numpy} only works
well with plain data arrays, hiding other metadata and attributes, for example
the \texttt{unit} of a \astropyQuantity. Consequently, a new \astropyMasked\
class was designed, based on a framework very similar to that of
\astropyDistribution, making it easy to create masked instances of other
classes.  In particular, \astropyMasked\ can be used to create masked quantities
for \astropyQTable, enabling I/O of masked data from different file types.

@@

Also part of \astropysubpkg{timeseries} are common analysis routines, including
\href{https://docs.astropy.org/en/stable/timeseries/lombscargle.html}{Lomb-Scargle}
and
\href{https://docs.astropy.org/en/stable/timeseries/bls.html}{box-least-squares}
periodogrammes.

\paragraph{Spectral Coordinates} Measurements are often taken at specific
``spectral coordinates,'' be they frequencies, wavelengths, or photon energies.
\astropyQuantity\ can represent these and convert between them via dedicated
equivalencies. The new \astropySpectralCoord\ builds on \astropyQuantity\ by
providing a more straightforward interface: baking in these equivalencies and
those for Doppler velocities. Furthermore, \astropySpectralCoord\ can be made
aware of the observer and target reference frames, allowing transformation from
telescope-centric (or topocentric) frames to Barycentric or Local Standard of
Rest (LSRK and LSRD) velocity frames.

@@

Units were also integrated further within \astropypkg. For an already-defined unit-less
\astropyModel, e.g. those imported from another library, \astropymodeling can
now coerce units.
% TODO! transition words
A new module – \astropycosmologyunits – has been added to the cosmology
sub-package for defining and collecting cosmological units and equivalencies.
The unit \texttt{littleh} and equivalency
\astropyapidoc{cosmology.units.with_H0}{with\_H0} was moved from the main
\astropyunits sub-package to \astropycosmologyunits. A new unit,
\texttt{redshift}, has been added for tracking factors of cosmological redshift.
To correctly use redshift units in dimensional analysis, \texttt{redshift} is
\astropyapi{cosmology.units.dimensionless_redshift}{treated as dimensionless}
by default. To convert between redshift and other cosmological distance
measures, e.g. CMB temperature or comoving distance, the equivalency
\astropyapidoc{cosmology.units.with_redshift}{with\_redshift}
has also been added. This equivalency is actually a composite of other equivalencies,
which may be used separately.

@@

Within \astropypkg and \python there are numerous ways to represent and store
array-valued data. Some of the differences are historical:
\astropyapidoc{table.Column}{table.Column} and
\astropyapidoc{io.fits.Column}{io.fits.Column} are not the same. Some
differences are computational: \package{numpy}, \package{cupy}, and
\package{dask} arrays have almost identical APIs, but are optimized for
different use cases. Lastly, some differences are inherent: \astropyQuantity,
\astropyTime\, and \astropySkyCoord\ represent fundamentally different types of
objects.

We aim to make it possible for any array-valued data to be used as a column in a
table. A well defined protocol for mixin-columns has been developed for
\astropytable, allowing the original object to be used as a column with a
familiar API, and to ``round-trip'' through tables with no loss of data or
attributes. With this protocol, it is now possible to store \astropy native
objects -- including \astropyTime, \astropyQuantity, and \astropySkyCoord --
within a \astropyTable and write these to various file formats, such as FITs.
For objects not already covered by the mixin protocol, functions can be
registered with \astropyTable\ to convert any array-like object into a mixin
column. As an example, the mixin functions are used to integrate \package{dask}
arrays with \astropyTable, allowing cloud-stored or cluster-scale data to be
used as a column in a \astropyTable.

@@

The FITS standard was extended to rigorously describe time coordinates in the
World Coordinate System (WCS) framework \citep{FITS-Time:2015}. Compared to
other types of coordinates in WCS, time requires more metadata: format, scale,
position, reference, etc. This metadata had to be manually specified and the
nuances understood by the user. \astropyfits could read this data as a standard
\astropyFitsColumn\, but would not interpret the time-related metadata and
attributes. Through the support of the
\href{https://summerofcode.withgoogle.com/archive/2017/projects/4778482366152704}{Google
Summer of Code} 2017 program\footnote{ To learn more about this project, please
see the final report,
\href{https://aaryapatil.wordpress.com/2017/08/28/a-mixin-protocol-for-seamless-interoperability/}{A
mixin protocol for seamless interoperability}}, the \astropyfits package now
interprets time data correctly, using \astropyTime\ as a `mixin' column.  For
backward compatibility with manual systems, this feature may be turned off.

@@

\astropy now supports reading and writing tables in the American Astronomical
Society Journals' Machine-Readable Table (MRT) format. This ASCII format has
long been missing and as added in this year's Google Summer of Code project adds
\href{https://docs.astropy.org/en/stable/io/ascii/write.html#cds-mrt-format}{MRT}
to \astropyTable\ I/O. In addition, \astropyTable\ may also read from and write
to \href{https://asdf-standard.readthedocs.io/en/latest/}{ASDF},
\href{https://docs.astropy.org/en/stable/io/unified.html#table-io-parquet}{Parquet},
and \href{https://wwwastro.msfc.nasa.gov/qdp/}{QDP} formats.

The \href{https://github.com/astropy/astropy-APEs/blob/main/APE6.rst}{ECSV
standard} has been updated to version 1.0, adding support three additional data
subtypes. First, it adds multidimensional column data (both masked and unmasked)
with fixed dimensions in all table cells. Second, it adds multidimensional
column data with variable-dimension arrays similar to FITS variable-length
arrays. Third, it adds object-type columns with simple \python objects.

@@

% TODO! better transition
\astropyiosubpkg{registry} is a powerful way to define input and output (I/O)
functions for \astropypkg objects, such as reading from or writing to a file,
following a given standard. \astropy uses this internally for the I/O methods in
\astropyTable\ and \astropyCosmology, and users can register custom I/O to
extend the options on these classes.

As of Astropy 5.0, the I/O registry submodule has been generalized to enable a
number of new use cases. for instance, the class-based architecture allows for
the creation of custom registries. One application is in \astropycosmology,
which has two different \textit{kinds} of registries for \astropyCosmology: one
for reading and writing files, and another for converting between python
objects. Using \astropyiosubpkg{registry} for custom classes means a developer
does not have to create a whole new I/O system and can offer to the user a
unified and familiar API.

@@

An important focus of \astropy has been to increase the precision and accuracy
of its functionality, while, where appropriate, making sure results obtained
using older versions of \astropypkg are reproducible. Within each section below
we include in our descriptions how old results may be reproduced. The primary
means are with options in configuration files and settings on runtime configuration
objects called \astropyScienceState. Notable improvements to \astropypkg have
been made to \astropytime, \astropyconstants, \astropycoordinates, and
\astropycosmology, and we describe each in turn.

@@

Measurements of physical constants (and the units defined from them) improve
over time. Periodically the standardized systems of units and constants are
updated to reflect these improvements. For instance, in 2019 the SI system was
redefined \citep{NIST2019}, with an accompanying update to the physical
constants in
\href{https://codata.org/initiatives/data-science-and-stewardship/fundamental-physical-constants/}{\texttt{SI/CODATA
2018}}. \astropyconstants now defaults to use the \texttt{SI/CODATA 2018}
values, with the units in \astropyunits based on these constants. Most of
\astropypkg and affiliate packages build upon \astropyunits, so this update
effects the entire \astropy ecosystem.

For reproducibility, \astropypkg allows the constants' (and therefore units')
definitions to be rolled back to prior values, e.g. to the \texttt{SI/CODATA
2014} values. For work sensitive to the values of the fundamental constants we
recommend including with the work an \astropy configuration file, which
specifies the set of constants used.

@@

Since \citealt{astropy:2018} the following cosmology realizations have been
added:
\href{http://docs.astropy.org/en/stable/api/astropy.cosmology.WMAP1.html}{WMAP First Year}
\citep{WMAP1Year:2003};
\href{http://docs.astropy.org/en/stable/api/astropy.cosmology.WMAP3.html}{WMAP
Three Year} \citep{WMAP3Year:2007};
\href{http://docs.astropy.org/en/stable/api/astropy.cosmology.Planck15.html}{Planck 2015}
\citep{Planck2015XIII:2016}; and the
\href{http://docs.astropy.org/en/stable/api/astropy.cosmology.Planck18.html}{Planck
2018} best-fit cosmological parameters \citep{Planck2018VI:2020}.

@@

Being able to describe the position of objects, i.e., their coordinates, is
fundamental across many knowledge domains. \astropycoordinates allows one to
work with low-level positional and velocity data all the way to high-level
coordinate objects with reference frames, atmospheric information, and more. A
central feature of \astropycoordinates is the ability to transform data between
reference frames, e.g. \astropyICRS\ \citep{ICRS:1997} to \astropyGalacticLSR\
\citep{GalacticLSR:2010}. However, there have been some historical limitations
for spatially proximate transformations, impacting the usefulness of
\astropycoordinates for ground-based telescopes and astronometry within the
solar system. Transformations in the \astropyAltAz\ frame were reasonably
precise for very distant objects, but wrong by up to several arcseconds for
e.g., the location of the moon. Now these transformations are much more precise,
down to the milliarcsecond level. Similar precision improvements were made to
the
\astropyapi{coordinates.builtin_frames.HADec}{Hour Angle-Declination}
frame transformations. Additionally,
\astropyapi{coordinates.builtin_frames.BaseEclipticFrame}{Ecliptic frames}
and associated transformations have been updated to correctly reflect the “true”
and “mean” terminology.

For Galactic astronomers, the \astropyGalactocentric\
\astropyapi{coordinates.galactocentric_frame_defaults}{frame defaults}
have been updated to include more recent measurements (tabulated in the
\href{https://docs.astropy.org/en/stable/api/astropy.coordinates.galactocentric_frame_defaults.html#astropy.coordinates.galactocentric_frame_defaults.references}{\texttt{frame\_defaults.references}}
attribute). For reproducibility, old definitions are still available.
